Matching bullets

### 2015-11-20 imaging-paper.Rnw
move sections around
figure outline of matching ...

\includegraphics[width=\columnwidth]{images/side-by-side-manual-match.png}
\caption{\label{fig:manualmatch}\hh{Manually adjusted side-by-side comparison of land five of bullet 1 and land 1 of bullet 2.}}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{images/matchup-rgl.png}
\caption{\label{fig:manualmatch}\hh{Different view of the manually adjusted side-by-side comparison of land five of bullet 1 and land 1 of bullet 2.}}
\end{figure}

>>>>

\includegraphics[width=\columnwidth]{images/side-by-side-manual-match.png}
\caption{\label{fig:manualmatch}\hh{Manually adjusted side-by-side comparison of land five of bullet 1 and land 1 of bullet 2.}}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{images/matchup-rgl.png}
\caption{\label{fig:manualmatch-rgl}\hh{Different view of the manually adjusted side-by-side comparison of land five of bullet 1 and land 1 of bullet 2.}}
\end{figure}

<<twolands100, cache=TRUE,  echo=FALSE>>=
images <- file.path(datadir, dir(datadir))

lof <- processBullets(paths = images[c(5,7)], x = 100)

subLOFx1 <- subset(lof, bullet=="Br1 Bullet 1-5")
subLOFx2 <- subset(lof, bullet=="Br1 Bullet 2-1")
subLOFx1$y <- subLOFx1$y + 19*1.5625 # working now!!!
lofX <- rbind(data.frame(subLOFx1), data.frame(subLOFx2))
@
\begin{figure}
\centering
    \subfloat[Crosscuts at $x = 100$.\label{fig:crosscut}]{%
<<crosscuts, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3, out.width='.49\\textwidth'>>=
qplot(y, resid, group=bullet, colour=bullet, data=lof, 
      geom="line", alpha=I(0.6)) + 
  scale_colour_brewer("", palette="Set1") + theme_bw() +
  theme(legend.position = c(.9, .2))
@
    }
    \hfill
    \subfloat[Adjusted (Bullet 1-5 horizontally shifted) crosscuts at $x = 100$.\label{fig:crosscutX}]{%
<<crosscutsX, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3, out.width='.49\\textwidth'>>=
qplot(y, resid, group=bullet, colour=bullet, data=lofX, 
      geom="line", alpha=I(0.6)) + 
  scale_colour_brewer(palette="Set1") + theme_bw() +
  theme(legend.position="none")
@
    }
\caption{\label{fig:cross100} Lines showing surface crosscuts at $x = 100$. A horizontal shift of the values of Bullet 1-5 to the right shows the similarity of the striation marks.}
\end{figure}

\hh{Using (for now) a single crosscut across the surface, we extract the values and remove the class characteristics using a loess fit as before. This enables us to focus on the individual characterists. Striation marks show up in this representations as peaks and valleys. Figure~\ref{fig:cross100} shows lines of the surface crosscut at $x = 100$. A horizontal shift of one of the lines (result shown in (b)) emphasizes the strong similarities.}

\begin{figure}
\centering
    \subfloat[Loess smooth at $x = 100$ (span is 0.03).\label{fig:smooth}]{%
<<smooth, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3, out.width='.49\\textwidth', warning=FALSE>>=
lofX <- lofX %>% group_by(bullet) %>% mutate(
  l30 = smoothloess(y, resid, span = 0.03)
)
lofX$r05 <- 0.75* sign(lofX$l30) * as.numeric(abs(lofX$l30) > .75)
lofX$type <- factor(lofX$r05)
levels(lofX$type) <- c("groove", NA, "peak")

qplot(data=lofX, y, resid, colour=bullet, size=I(1)) +
  geom_line(aes(y=l30), colour="grey30") +
  facet_grid(bullet~.) +
  scale_colour_brewer("", palette="Set1") +
  theme_bw() +
  theme(legend.position="none")
@
    }
    \hfill
    \subfloat[Values above/below a threshold level are defined as peaks and grooves. \label{fig:smoothcutb}]{%
<<smoothcut, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=4, out.width='.49\\textwidth', warning=FALSE>>=
qplot(data=lofX, x=y, y=l30, colour=type, geom="line", group=bullet) + 
  facet_grid(bullet~.) +
  ylab("Individual characteristics") + 
  geom_point(aes(y=r05)) +
  scale_colour_brewer(palette="Set2", na.value = "grey90") +
  theme_bw() +
  theme(legend.position="bottom")
@
    }
\hfill
    \subfloat[ \label{fig:smoothcutc}]{%
<<smoothtile, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=2.5, out.width='.49\\textwidth'>>=
qplot(data=lofX, x=y, y=bullet, fill=type, geom="tile") +
  scale_fill_brewer(palette="Set2", na.value="grey90") + 
  theme_bw() +
  ylab("") +
  theme(legend.position="bottom")
@
    }    
\caption{\label{fig:smoothcut} Processing surface crosscuts.}
\end{figure}
